---
title: "Mini Project - 1"
author: "S17490_WPK Thamishka"
date: "2023-05-23"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load the Data set
```{r}
ds_salaries <- read.csv("~/Desktop/4th Year_I/ST405 - Multivariate Methods II (2)/Mini Project/Mini Project/ds_salaries.csv")
head(ds_salaries)
```
# Details about Data Set

work_year: The year the salary was paid.

experience_level: The experience level in the job during the year
  EN: Entry-level or Beginner
  EX: Experienced or Intermediate
  MI: Mid-level or Mid-career
  SE: Senior or Expert

employment_type: The type of employment for the role
  CT: Contract
  FL: Freelance
  FT: Full-Time
  PT: Part-Time

job_title: The role worked in during the year.

salary: The total gross salary amount paid.

salary_currency: The currency of the salary paid as an ISO 4217 currency code.
  AUD: Australian Dollar
  BRL: Brazilian Real
  CAD: Canadian Dollar
  CHF: Swiss Franc
  CLP: Chilean Peso
  CZK: Czech Koruna
  DKK: Danish Krone
  EUR: Euro
  GBP: British Pound
  HKD: Hong Kong Dollar
  HUF: Hungarian Forint
  ILS: Israeli Shekel
  INR: Indian Rupee
  JPY: Japanese Yen
  MXN: Mexican Peso
  PLN: Polish Złoty
  SGD: Singapore Dollar
  THB: Thai Baht
  TRY: Turkish Lira
  USD: United States Dollar

salaryinusd: The salary in USD

employee_residence: Employee's primary country of residence in during the work year as an ISO 3166 country code.
  AE: United Arab Emirates
  AM: Armenia
  AR: Argentina
  AS: American Samoa
  AT: Austria
  AU: Australia
  BA: Bosnia and Herzegovina
  BE: Belgium
  BG: Bulgaria
  BO: Bolivia
  BR: Brazil
  CA: Canada
  CF: Central African Republic
  CH: Switzerland
  CL: Chile
  CN: China
  CO: Colombia
  CR: Costa Rica
  CY: Cyprus
  CZ: Czech Republic
  DE: Germany
  DK: Denmark
  DO: Dominican Republic
  DZ: Algeria
  EE: Estonia
  EG: Egypt
  ES: Spain
  FI: Finland
  FR: France
  GB: United Kingdom (Great Britain)
  GH: Ghana
  GR: Greece
  HK: Hong Kong
  HN: Honduras
  HR: Croatia
  HU: Hungary
  ID: Indonesia
  IE: Ireland
  IL: Israel
  IN: India
  IQ: Iraq
  IR: Iran
  IT: Italy
  JE: Jersey
  JP: Japan
  KE: Kenya
  KW: Kuwait
  LT: Lithuania
  LU: Luxembourg
  LV: Latvia
  MA: Morocco
  MD: Moldova
  MK: North Macedonia
  MT: Malta
  MX: Mexico
  MY: Malaysia
  NG: Nigeria
  NL: Netherlands
  NZ: New Zealand
  PH: Philippines
  PK: Pakistan
  PL: Poland
  PR: Puerto Rico
  PT: Portugal
  RO: Romania
  RS: Serbia
  RU: Russia
  SE: Sweden
  SG: Singapore
  SI: Slovenia
  SK: Slovakia
  TH: Thailand
  TN: Tunisia
  TR: Turkey
  UA: Ukraine
  US: United States
  UZ: Uzbekistan
  VN: Vietnam

remote_ratio: The overall amount of work done remotely

company_location: The country of the employer's main office or contracting branch
  AE: United Arab Emirates
  AL: Albania
  AM: Armenia
  AR: Argentina
  AS: American Samoa
  AT: Austria
  AU: Australia
  BA: Bosnia and Herzegovina
  BE: Belgium
  BO: Bolivia
  BR: Brazil
  BS: The Bahamas
  CA: Canada
  CF: Central African Republic
  CH: Switzerland
  CL: Chile
  CN: China
  CO: Colombia
  CR: Costa Rica
  CZ: Czech Republic
  DE: Germany
  DK: Denmark
  DZ: Algeria
  EE: Estonia
  EG: Egypt
  ES: Spain
  FI: Finland
  FR: France
  GB: United Kingdom (Great Britain)
  GH: Ghana
  GR: Greece
  HK: Hong Kong
  HN: Honduras
  HR: Croatia
  HU: Hungary
  ID: Indonesia
  IE: Ireland
  IL: Israel
  IN: India
  IQ: Iraq
  IR: Iran
  IT: Italy
  JP: Japan
  KE: Kenya
  LT: Lithuania
  LU: Luxembourg
  LV: Latvia
  MA: Morocco
  MD: Moldova
  MK: North Macedonia
  MT: Malta
  MX: Mexico
  MY: Malaysia
  NG: Nigeria
  NL: Netherlands
  NZ: New Zealand
  PH: Philippines
  PK: Pakistan
  PL: Poland
  PR: Puerto Rico
  PT: Portugal
  RO: Romania
  RU: Russia
  SE: Sweden
  SG: Singapore
  SI: Slovenia
  SK: Slovakia
  TH: Thailand
  TR: Turkey
  UA: Ukraine
  US: United States
  VN: Vietnam
  
company_size: The median number of people that worked for the company during the year
  L : Large
  M : Medium
  S : Small

# Descriptive Analysis 
```{r}
str(ds_salaries)
```
## Find null values

```{r}
summary(colSums(is.na(ds_salaries)))
colSums(is.na(ds_salaries))
```

## Find the duplicates
```{r}
# Find duplicates in the dataset
duplicates <- duplicated(ds_salaries)

# Subset the dataset to remove duplicates
unique_data <- ds_salaries[!duplicates, ]

# Print the unique dataset without duplicates
ds_salaries <- unique_data
```

```{r}
dim(ds_salaries)
```

## Convert Categorical to factors

```{r}
convert_categorical_to_levels <- function(dataset) {
  for (col in colnames(dataset)) {
    if (is.factor(dataset[[col]]) || is.character(dataset[[col]])) {
      dataset[[col]] <- factor(dataset[[col]])
    }
  }
  return(dataset)
}

# Example usage
ds_salaries <- convert_categorical_to_levels(ds_salaries)
```

```{r}
str(ds_salaries)
```
## Load Libraries

```{r}
library(FactoMineR)
library(factoextra)
library(foreign)
library(psych)
library(lavaan)
library(semPlot)
```

## Convert factors to numerical

```{r}
convert_categorical_to_numeric <- function(dataset) {
  for (col in colnames(dataset)) {
    if (is.factor(dataset[[col]]) || is.character(dataset[[col]])) {
      dataset[[col]] <- as.numeric(dataset[[col]])
    }
  }
  return(dataset)
}

# Example usage
ds_salaries1 <- convert_categorical_to_numeric(ds_salaries)
```

```{r}
str(ds_salaries1)
```

## Applt KMO

```{r}
psych::KMO(ds_salaries1)
```
## Apply Bartlett Test

```{r}
psych::cortest.bartlett(ds_salaries1)
```
## Apply Parallel to find factors and componets

```{r}
psych::fa.parallel(ds_salaries1)
```
## PCA

```{r}
model_pca <- psych::principal(ds_salaries1, nfactors = 4)
```

```{r}
coms <- model_pca$communality
round(coms, 2)
```
```{r}
model_pca
```
## EFA

```{r}
library(GPArotation)
model_fa <- fa(ds_salaries1, nfactors = 4) 
model_fa
```

## CFA

```{r}
syntx <- '
  RC1 =~ salary_currency + salary_in_usd + employee_residence + company_location
  RC2 =~ work_year + employment_type + remote_ratio
  RC4 =~ salary + company_size
  RC3 =~ employment_type + job_title

  SAQ =~ RC1
  SAQ =~ RC2
  SAQ =~ RC4
  SAQ =~ RC3
  '

model_cfa <- lavaan::cfa(syntx, data = ds_salaries1)
model_cfa
```
```{r}
varTable(model_cfa)

```

```{r}
summary(model_cfa, fit.measures = TRUE, standardized = TRUE)
```


```{r}
fits <- fitMeasures(model_cfa)
data.frame(fits = round(fits, 2))
```

```{r}
semPlot::semPaths(model_cfa, what = "est", rotation = 2, 
  style = "lisrel", font = 2)  
title("Row Estimations")
```
```{r}
semPlot::semPaths(model_cfa, what = "std", rotation = 2, 
  style = "lisrel", font = 2, title = TRUE)
title("Standardized Estimations")
```

